Fast, Scalable Phrase-Based SMT Decoding

### 2016-03-18 acl.2016/acl2016.tex
acl

The objective of decoding is to find the target translation with the maximum probability, given a source sentence. That is, for a source sentence $s$, the objective is to find a target translation $\hat{t}$ which has the highest conditional probability $p(t | s)$. Mathematically, this is written as:
\begin{equation}
\hat{t} = \arg \max_t p( t | s )
\label{eq:argmax-factored-trans}
\end{equation}
where the \emph{arg max} function is the search. The log-linear model generalizes Equation~\ref{eq:argmax-factored-trans} to include more component models and weighting each model according to the contribution of each model to the total probability. 
\begin{equation}
\label{eq:Log-Linear}
p(t | s) 	=  \frac{1}{Z} \exp ( \sum_m \lambda_m h_m ( t, s)^{} )
\end{equation}
where $\lambda_m$ is the weight, and $h_m$ is the feature function, or `score', for model $m$. $Z$ is the partition function which can be ignored for optimization.

@@

A translation of a source sentence is created by applying a series of translation rules which together translate each source word once, and only once. Each partial translation is called a \emph{hypothesis}, which is created by applying a rule to an existing hypothesis. This process is called \emph{hypothesis expansion} and starts with a hypothesis that has translated no source word and ends with a completed hypothesis that has translated all source words. The highest-scoring completed hypothesis, according to the model score, is returned as  most probable translation, $\hat{t} $. Incomplete hypotheses are referred to as partial hypotheses.

Each rule translates a contiguous sequence of source words but successive translation options do not have to be adjacent on the source side, depending on the distortion limit. However, the target output is constructed strictly left-to-right from the target string of successive translation options. Therefore, successive translation options which are not adjacent and monotonic in the source causes translation reordering.

A beam search algorithm is used to create the completed hypothesis set efficiently. Partial hypotheses are organized into stacks where each stack holds a number of comparable hypotheses. Hypotheses in the same stack have the same coverage cardinality $|C|$, where $C$ is  the coverage set, $C \subseteq \{1,2,... |s| \} $ of the number of  source words translated. Therefore, $|s| + 1$ number of stacks are created for the decoding of a sentence $s$.

There are three main optimization to the search that we shall investigate. Firstly, the search creates and destroy a large number of hypothesis objects in memory which puts a heavy burden on the operating system. We shall optimize the search algorithm to use memory pools and object pools, replacing the operating system's general purpose memory management with our own application-aware management.

In multiprocessor servers, the CPU cache is attached to each processor and each core. If a sentences is being decoded on one CPU is switched to another, the CPU cache on the new CPU must be repopulated, slowing down decoding. We will therefore investigate binding threads to specific cores.

Lastly, we shall investigate different stack configurations other than coverage cardinality to see whether they can improve speed and translation quality.

@@

>>>>

The objective of decoding is to find the target translation with the maximum probability, given a source sentence. That is, for a source sentence $s$, the objective is to find a target translation $\hat{t}$ which has the highest conditional probability $p(t | s)$. Formally, this is written as:
\begin{equation}
\hat{t} = \arg \max_t p( t | s )
\label{eq:argmax-factored-trans}
\end{equation}
where the \emph{arg max} function is the search. The log-linear model generalizes Equation~\ref{eq:argmax-factored-trans} to include more component models and weighting each model according to the contribution of each model to the total probability. 
\begin{equation}
\label{eq:Log-Linear}
p(t | s) 	=  \frac{1}{Z} \exp ( \sum_m \lambda_m h_m ( t, s)^{} )
\end{equation}
where $\lambda_m$ is the weight, and $h_m$ is the feature function, or `score', for model $m$. $Z$ is the partition function which can be ignored for optimization.

@@

A translation of a source sentence is created by applying a series of translation rules which together translate each source word once, and only once. Each partial translation is known as a \emph{hypothesis}, which is created by applying a rule to an existing hypothesis. This process is called \emph{hypothesis expansion} and starts with a hypothesis that has translated no source word and ends with a completed hypotheses that have translated all source words. The highest-scoring completed hypothesis, according to the model score, is returned as  most probable translation, $\hat{t} $.

In the phrase-based model, each rule translates a contiguous sequence of source words but successive translation options do not have to be adjacent on the source side, depending on the distortion limit. The target output is constructed strictly left-to-right from the target side of successive translation rules.

A beam search algorithm is used to create the completed hypothesis set efficiently. Partial translations are organized into stacks where each stack holds a number of comparable hypotheses. Most phrase-based implementations place hypotheses in the same stack that have the same coverage cardinality $|C|$, where $C$ is  the coverage set, $C \subseteq \{1,2,... |s| \} $ of the number of  source words translated.

@@

\section{Proposed Improvements}

There are four main optimizations that we shall investigate. Firstly, the search creates and destroy a large number of hypothesis objects in memory which puts a burden on the operating system. We shall optimize the search algorithm to use memory pools and object pools, replacing the operating system's general purpose memory management with our own application-aware management.

%In multiprocessor servers, the CPU cache is attached to each processor and each core. If a sentences is being decoded on one CPU is switched to another, the CPU cache on the new CPU must be repopulated, slowing down decoding. We will therefore investigate binding threads to specific cores.

Secondly, we shall investigate different stack configurations other than coverage cardinality to see whether they can improve speed and translation quality.
